---
title: "Daipark_ch1"  
author: "Baek, Jong min"  
date: "`r Sys.Date()`"  
output:   
  pdf_document:
    fig_caption: false  
    latex_engine: xelatex
    highlight: haddock  
    keep_tex: true  
    includes:
      in_header: rmd-pdf-support/latex-topmatter.tex
    # pandoc_args: [
    #  "-V", "classoption=twocolumn"
    toc: true   
    toc_depth: 2  
    # number_sections: true  
monofont: Consolas
smaller: yes
classoption: a4paper
---
```{r setup, include=FALSE}
library(rmarkdown)

knitr::opts_chunk$set(echo = TRUE) # 코드를 보여준다.
knitr::opts_chunk$set(background = '718CBA')  # ??
```

\newpage
## Exercise 9.  

a) uniform distribution from 10 to 15 cameras a month. If 12 cameras are ordered at the beginning of a month, what are the expected overstock cost and the expected undercost or shortage cost? What is the expected total cost?   

\begin{align*}
C_o &= cost - salvage \\
    &= inventory \, holding \, cost + wholesale \, cost  \\
    &= 480+25-0 = 505 \\
C_u &= price - cost \\
    &= retail \, price + special \, delivery \, charge - wholesale \, cost \\
    &= 600 + 50 - 480 = 170
\end{align*}

\begin{align*}
\mathbb{E}[(12-D)^+] &= \int_{10}^{12}(12-x)^+\frac{1}{5}dx + \int_{12}^{15}(12-x)^+\frac{1}{5}dx \\
                     &=\frac{14}{5} \\
\mathbb{E}[(D-12)^+] &=\int_{10}^{12}(x-12)^+\frac{1}{5}dx + \int_{12}^{15}(x-12)^+\frac{1}{5}dx \\
                     &=\frac{1}{2}
\end{align*}

Expected over cost = $505 \times \frac{14}{5}$ = 1414  
Expected under cost = $170 \times \frac{1}{2}$ = 85  
Expected total cost = 1414+85= 1499
\vspace{5pt}

b) What is optimal number of cameras to order to minimize the expected total cost?

\begin{align*}
y^* &= \frac{x-10}{15-10} = \frac{67}{125} \\
    &= 12.68 = 12
\end{align*}


<!-- \vspace{5pt} -->

c) Assume that the demand can be approximated by a normal distribution with mean 1000 and standard deviation 100 cameras a month. What is the optimal number of cameras to order to minimize the expected total cost?

$N(\mu,\sigma^2) = N(1000,100^2)$  

```{r}
qnorm(0.25185,mean=1000,sd=100)
```

\newpage

## Exercise 10

a) What is the optimal ordering quantity for each case when the demand is discrete with $Pr{\{D = 500}\} = Pr{\{D = 800}\} =1/8$, $Pr{\{D = 600}\}=1/2  and Pr{\{D = 700}\} = 1/4$?  

$C_u = 100(shortage \,cost)$    
$C_0 = 50(the \, solvent\, cost(40) +disposal \, charge(10))$  
$F(D) \geq \frac{100}{100+50}(\frac{2}{3})$

\begin{center}
\begin{tabular}{c|c|c|c|c}
  \hline
  $d$ & 500 & 600 & 700 & 800 \\ \hline
  $\mathbb{P}[D = d]$ & $\frac{1}{8}$ & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{8}$  \\
  $\mathbb{P}[D \leq d]$ & $\frac{1}{8}$ & $\frac{5}{8}$ & $\frac{7}{8}$ & $\frac{8}{8}$ \\ \hline
\end{tabular}
\end{center}

\vspace{10pt}

\begin{text}
\\
$F(500) = \frac{1}{8}(0.125) \qquad \qquad \qquad < \frac{2}{3}(0.66)$ \\
$F(600) =\frac{1}{8}+\frac{1}{2}= \frac{5}{8}(0.625) \qquad < \frac{2}{3}(0.66)$  \\
$F(700) = \frac{1}{8}+\frac{1}{2}+\frac{1}{4} =\frac{7}{8}(0.875) \qquad > \frac{2}{3}(0.66)$ \\
$F(800) = \frac{1}{8}+\frac{1}{2}+\frac{1}{4} + \frac{1}{8} =\frac{8}{8}(1.0) \qquad > \frac{2}{3}(0.66)$ \\
\\
The optimal order quantity $y^* = 700$  \\
\end{text}

b) What is the optimal ordering policy for arbitrary initial inventory level m? (You need to specify the critical value $m^*$ in addition to the optimal order-up-to quantity $y^*$. When $m \leq m^*$, you make an order. Otherwise, do not order. )  

m(prepared inventory) is 0, 100, 300, 500 and 700  
d(demand) is 500, 600, 700, 800  
\vspace{10pt}

\begin{center}
\begin{tabular}{c|c|c|c|c}
  \hline
  $d$ & 500 & 600 & 700 & 800 \\ \hline
  $\mathbb{P}[D = d]$ & $\frac{1}{8}$ & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{8}$  \\
  $\mathbb{P}[D \leq d]$ & $\frac{1}{8}$ & $\frac{5}{8}$ & $\frac{7}{8}$ & $\frac{8}{8}$ \\
  $(D-m)^+(m=0)$ & 500 & 600 & 700 & 800 \\
  $(D-m)^+(m=100)$ & 400 & 500 & 600 & 700 \\
  $(D-m)^+(m=300)$ & 200 & 300 & 400 & 500 \\
  $(D-m)^+(m=500)$ & 0 & 100 & 200 & 300 \\
  $(D-m)^+(m=700)$ & 0 & 0 & 0 & 100 \\
  $(m-d)^+(m=0)$ & 500 & 600 & 700 & 800 \\
  $(m-d)^+(m=100)$ & 0 & 0 & 0 & 0 \\
  $(m-d)^+(m=300)$ & 0 & 0 & 0 & 0 \\
  $(m-d)^+(m=500)$ & 0 & 0 & 0 & 0 \\
  $(m-d)^+(m=700)$ & 200 & 100 & 0 & 0 \\ \hline
\end{tabular}
\end{center}


\newpage

c) Assume optimal quantity will be orderd. What is the total expected cost when the initial inventory m = 0? what is the total expected cost when the initial inventory m = 700?  

\vspace{10pt}

Daipark_ch1.Rmd
```{r}
"Hello"
```

