---
title: "A1_solution"  
author: "Bong Seok Kim"  
date: "`r Sys.Date()`"  
output:   
  pdf_document:  
    latex_engine: xelatex
    highlight: haddock  
    keep_tex: true  
    includes:
      in_header: rmd-pdf-support/latex-topmatter.tex
    # pandoc_args: [
    #  "-V", "classoption=twocolumn"
    # ]
    toc: true   
    toc_depth: 2  
    # number_sections: true  
monofont: Consolas
smaller: yes
classoption: a4paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(background = '718CBA')  
```


## Exercise 11
Solve following and express $\pi_i$ for $i=0,1,2,...$
\begin{eqnarray}
\pi_0 + \pi_1 + \pi_2 +... &=& 1 \nonumber\\
0.02 \pi_0 + 0.02 \pi_1 + 0.02 \pi_2 + ... &=& \pi_0 \nonumber\\
0.98 \pi_0 &=& \pi_1 \nonumber\\
0.98 \pi_1 &=& \pi_2 \nonumber\\
0.98 \pi_2 &=& \pi_3 \nonumber\\
...&=&... \nonumber
\end{eqnarray}

### Solution:

\begin{eqnarray}
\pi_0 + \pi_1 + \pi_2 +... &=& 1 \\
0.02 \pi_0 + 0.02 \pi_1 + 0.02 \pi_2 + ... &=& \pi_0 \\
0.98 \pi_0 &=& \pi_1 \\
0.98 \pi_1 &=& \pi_2 \\
0.98 \pi_2 &=& \pi_3 \\
...&=&... \nonumber
\end{eqnarray}


From (3)-(5), 

\begin{eqnarray}
\pi_1 &=& (0.98)\pi_0 \nonumber\\
\pi_2 &=& (0.98)\pi_1 = (0.98)^2 \pi_0 \nonumber\\
\pi_3 &=& (0.98)\pi_2 = (0.98)^3 \pi_0 \nonumber\\
\pi_i &=& (0.98)^i \pi_0\nonumber
\end{eqnarray}

Thus (1), becomes 

\begin{eqnarray*}
\pi_0 + \pi_1 + \pi_2 +... &=& \pi_0(1+0.98+0.98^2 + ...) \nonumber\\
\pi_0 (\frac{1}{1-0.98})) &=& 1 \nonumber\\
\pi_0 &=& 0.02\nonumber\\
\therefore \pi_i &=& (0.02)(0.98)^i \nonumber
\end{eqnarray*}

\newpage 

## Excercise 12 (Infinite geometric series)

Simplify the following. When $|r|<1$, $S=a+ar+ar^2+ar^3+...$

### Solution :

\setcounter{equation}{0}

\begin{eqnarray}
S  &=& a+ar^2+ar^3+...      \\
rS &=&   ar^2+ar^3+ar^4+...  \\
\nonumber
\end{eqnarray}

Subtract (1) and (2)

$(1-r)S = a$

$\therefore   S = \frac{a}{1-r}$




```{r message=FALSE, warning=FALSE, paged.print=TRUE}
"Done, Lecture A5. Simulation 2 "
```
