---
title: "Lecture C3. Discrete Time Markov Chain 3"  
author: "Reinforcement Learning Study"  
date: "`r Sys.Date()`"  
output:   
  pdf_document:  
    latex_engine: xelatex
    highlight: haddock  
    keep_tex: true  
    includes:
      in_header: rmd-pdf-support/latex-topmatter.tex
    # pandoc_args: [
    #  "-V", "classoption=twocolumn"
    # ]
    toc: true   
    toc_depth: 2  
    # number_sections: true  
monofont: Consolas
smaller: yes
classoption: a4paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(background = '718CBA')  
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#library(reticulate)
#matplotlib <- import("matplotlib")
#matplotlib$use("Agg", force = TRUE)
```

## Example 1

### Trainsition Matrix :

\begin{align*}
  P=
  \begin{pmatrix}
    &1/2& 1/2& 0& \\
    &1/2& 1/4&  1/4& \\ 
    &0& 1/3& 2/3&\\
  \end{pmatrix}
\end{align*}

### Trainsition Diagram : 

\begin{figure}[ht]
\centering
   \includegraphics[width=10cm]{example1.png}
   \hfil
\caption{Example 1 Trainsition Diagram}
\label{Figure 1.}
\end{figure}

\vspace{20pt}

### Remark
* A state $i$ is said to be recurrent if, starting from $i$, the probability of getting back to $i$ is 1 

* A state $i$ is said to be trainsient if, starting from $i$, the probability of getting back to $i$ is less than 1 

recurrent state :{1,2,3} ,All states communicate, all states recurrent

\newpage

## Example 2

### Trainsition Matrix :

\begin{align*}
  P=
  \begin{pmatrix}
    &1 & 0& 0& \\
    &1/4& 1/2&  1/4& \\ 
    &0& 0& 1\\
  \end{pmatrix}
\end{align*}

### Trainsition Diagram : 

\begin{figure}[ht]
\centering
   \includegraphics[width=10cm]{example2.png}
   \hfil
\caption{Example 2 Trainsition Diagram}
\label{Figure 2.}
\end{figure}

\vspace{20pt}

### Remark
* A state $i$ is said to be recurrent if, starting from $i$, the probability of getting back to $i$ is 1 

* A state $i$ is said to be trainsient if, starting from $i$, the probability of getting back to $i$ is less than 1 

* A state $i$ is said to be abosrbing state, as a special case of reccurent state, if $P_ii=1$ (You can naver leave the state $i$ if you get there) 



recurrent state : {1,3}

trainsient state : {2} 

abosrbing state : {1,3}


\newpage

## Example 3

### Trainsition Matrix :

\begin{align*}
  P=
  \begin{pmatrix}
    &1 & 0& 0& \\
    &1/3& 1/2&  1/6& \\ 
    &0& 0& 1\\
  \end{pmatrix}
\end{align*}

### Trainsition Diagram : 

\begin{figure}[ht]
\centering
   \includegraphics[width=10cm]{example3.png}
   \hfil
\caption{Example 3 Trainsition Diagram}
\label{Figure 3.}
\end{figure}

\vspace{20pt}

### Remark
* A state $i$ is said to be recurrent if, starting from $i$, the probability of getting back to $i$ is 1 

* A state $i$ is said to be trainsient if, starting from $i$, the probability of getting back to $i$ is less than 1 

* A state $i$ is said to be abosrbing state, as a special case of reccurent state, if $P_ii=1$ (You can naver leave the state $i$ if you get there) 



recurrent state : {1,3}

trainsient state : {2} 

abosrbing state : {1,3}

\newpage 

## Example 4

### Trainsition Matrix :

\begin{align*}
  P=
  \begin{pmatrix}
    &1/2 &1/2 & 0 &0 \\
    &1/2 &1/2 & 0 &0 \\ 
    &1/4 &1/4 &1/4 &1/4\\
    &0   &0 &0 &1\\
  \end{pmatrix}
\end{align*}

### Trainsition Diagram : 

\begin{figure}[ht]
\centering
   \includegraphics[width=10cm]{example4.png}
   \hfil
\caption{Example 4 Trainsition Diagram}
\label{Figure 4.}
\end{figure}

\vspace{20pt}

### Remark
* A state $i$ is said to be recurrent if, starting from $i$, the probability of getting back to $i$ is 1 

* A state $i$ is said to be trainsient if, starting from $i$, the probability of getting back to $i$ is less than 1 

* A state $i$ is said to be abosrbing state, as a special case of reccurent state, if $P_ii=1$ (You can naver leave the state $i$ if you get there) 



recurrent state : {1,2}

trainsient state : {3} 

abosrbing state : {4}











```{r message=FALSE, warning=FALSE, paged.print=TRUE}
"Done, Lecture C2. Discrete Time Markov Chain2 "
```